---
title: '**Welcome to Ordinary Differential Equation!**'
author: |
  | MTH-321 Section B
  | Fall 2023
  | University of Portland
  | Alex John Quijano
bibliography: references.bib
csl: apa.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source(file.path("R","functions.R"))
```

```{r echo=FALSE}
create_footer()
```

<br>

## **Quick Content Guide**

| Page                      | Contents                                                                          |
|---------------------------|-----------------------------------------------------------------------------------|
| [Home](index.html)        | Quick course and instructor information                                           |
| [Syllabus](syllabus.html) | About the class, class materials and resources, class assessment and expectations |
| [Topics](topics.html)     | Tentative topics, notes, assignments, and books and online resources list         |

<br>

## **Quick Course Information**

### Course Information

> * Title: MTH 321: Ordinary Differential Equation
> * Section: B

### Instructor Information

> * Instructor: Dr. Alex John Quijano
> * Office: Buckley Center 279
> * Email: quijano@up.edu

### Lectures and Discussions

> The course schedule and location is:
>
> * TuTh 9:45 AM - 11:10 AM, Franz Hall 222

<br>

## **Quick Academic Support**

### Walk-In Help Hours

> Dr. Alex John Quijano
> 
> * Walk-in TuTh at 2:00 PM - 3:25 PM, Buckley Center 279

### Appointment-Based Sessions

> Dr. Alex John Quijano
>
> <!-- Calendly inline widget begin -->
<div class="calendly-inline-widget" data-url="https://calendly.com/alexjohnquijano?hide_landing_page_details=1&hide_gdpr_banner=1" style="min-width:auto;height:650px;"></div>
<script type="text/javascript" src="https://assets.calendly.com/assets/external/widget.js" async></script>
<!-- Calendly inline widget end -->

### The Learning Commons

Students can get academic assistance through Learning Commons tutoring services and workshops. The Co-Pilot peer tutoring program provides students with opportunities to work with other students to get help in writing, math, group projects, and other courses. Schedule an appointment to meet with a Co-Pilot (tutor) by visiting the [Learning Commons](www.up.edu/learningcommons){target="_blank"} website. Students can also meet with a Co-Pilot during drop-in hours. Check the Learning Commons website or drop by the Learning Commons in BC 163 to learn more about their services. Find a tutor at the Learning Commons to get support on your academic journey.

### Math Resource Center

Appointment-based tutoring accepts appointments starting week 1 and sessions start week 2. Visit the [Math Resource Center](https://www.up.edu/learningcommons/math-resource-center/index.html){target="_blank"} website to sign-up for an appointment. Drop-in tutoring is Monday to Thursday, 3:00 PM - 6:30 PM in BC 163 and starts week 2. Check the Math Resource Center website or drop by the center for more information.

<br>

## **Quick Resources**

### Microsoft Teams

> The Teams for this course is [MTH-321B-fa23](https://teams.microsoft.com/l/team/19%3amUjnRz_6XSOvPw3cl7w_Jy5Zv02paMe1-GnIhfqZOmQ1%40thread.tacv2/conversations?groupId=98574745-3bc3-4ea7-be0e-12d8a3571769&tenantId=ea8f3949-231c-40b6-a33f-56873af96f87){target="_blank"}. If you need the Teams code, use **enn1e1s**.

### Computational Tools

We will be using these two computational tools in some assignments. These tools are free and open-source.

* **Geobra**

  > Geobra lesson links will be provided ad hoc.

* **Programming Languages**

  > R or Python instructions and materials will be provided ad hoc.

### Email

My UP email is quijano@up.edu. 

> If you prefer communicating through email, note that I have set up an email filter for this course, and you must put the “MTH 321” keyword in your subject line. 

<br>
