---
title: "Tentative Topics Schedule"
author: |
  | MTH-321 Section B
  | Fall 2023
  | University of Portland
  | Alex John Quijano
bibliography: references.bib
csl: apa.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source(file.path("R","functions.R"))
```

```{r echo=FALSE}
create_footer()
```

<br>

> See Books & Online Resources Lists for the reading materials.
>
> The readings are not mandatory but it is encouraged.

<br>The "Reading" column in the table below contains page number on which it refers to a label in the Books & Online Resources List. For example "Pgs. 1-5 [H]" refers to pages 1-5 of the first item in the list, which is the textbook titled "Ordinary Differential Equations: A Primer on Dynamics and Systems".

<br>Most of the materials (worksheets and homework) of each topic was taken from Inquiry oriented differential equations (IODE) by @iode2018.

<br>

## **Topics and Materials**

| **Week** | **Day** | **Topic** | **Activity** | **Homework** | **Reading** |
|---|---|:---:|---|---|---|
| **1** | Tu 8/29 | Introduction & Orientation to Ordinary Differential Equations (ODEs) | Calculus Review | - | Syllabus |
|  | Th 8/31 | [Modeling Physical Processes,<br>Classification of Equations, &<br>Verifying Solutions](class-notes/Modeling Physical Processes, Classification of Equations, & Verifying Solutions.pdf){target="_blank"} | Qualitative & Graphical Approaches| Assigned: Homework 1 | - |
| **2** | Tu 9/5 | [Graphical Approaches,<br>Equilibrium Stability, &<br>Numerical Solutions](class-notes/Equilibrium, Stability, & Numerical Solutions.pdf){target="_blank"} | A Numerical Approach | - | - |
|  | Th 9/7 | [Initial Value Problem (IVP),<br>Types of Solutions, &<br>Analytical Solutions](class-notes/Initial Value Problem, Types of Solutions, & Analytical Solutions.pdf){target="_blank"} | An Analytic Approach | Assigned: Homework 2 | - |
| **3** | Tu 9/12 | [Solving 1st Order ODEs](class-notes/Solving 1st Order ODEs.pdf){target="_blank"} | Linear Differential Equations | - | - |
|  | Th 9/14 | [Existence and Uniqueness of 1st Order IVP](class-notes/Existence and Uniqueness of 1st-Order IVP.pdf){target="_blank"} | Uniqueness of Solutions | Assigned: Homework 3 | - |
| **4** | Tu 9/19 | [Analyzing Autonomous 1st-Order ODEs](class-notes/Analyzing Autonomous 1st-Order ODEs.pdf){target="_blank"} | Modeling with Autonomous Differential Equations | - | - |
|  | Th 9/21 | [Bifurcations in One Dimension](class-notes/Bifurcations in One Dimension of 1st-Order ODEs.pdf){target="_blank"} | Varying a Parameter in Autonomous Differential Equations |  - | - |
| **5** | Tu 9/26 | Review | Exam 1 Examples | - | Exam 1 Guide |
|  | Th 9/28 | **Exam 1** | - | - | - |
| **6** | Tu 10/3 | [Systems of 1st-Order ODEs](class-notes/Systems of 1st-Order ODEs.pdf){target="_blank"} | Introduction to Systems | - | - |
|  | Th 10/5 | [Qualitative & Graphical Approaches of 1st-Order Linear Systems](class-notes/Qualitative & Graphical Approaches of 1st-Order Linear Systems.pdf){target="_blank"} | Spring Mass System and Linear Systems | - | - |
| **7** | Tu 10/10 | [Real & Complex Exponential Solutions of 1st-Order Linear Systems](class-notes/Real & Complex Exponential Solutions of 1st-Order Linear Systems.pdf){target="_blank"} | Damped and Undamped Linear Systems | - | - |
|  | Th 10/12 | *Cancelled* | - | Assigned: Homework 4 | - |
| **8** | Tu 10/17 | _Fall Break_ | - | - | - |
|  | Th 10/19 | _Fall Break_ | - | - | - |
| **9** | Tu 10/24 | [Eigentheory & Equilibrium of 1st-Order Linear Systems](class-notes/Eigentheory & Equilibrium of 1st-Order Linear Systems.pdf){target="_blank"} | Eigentheory Applied to Linear Systems | - | - |
|  | Th 10/26 | [Stability Analysis of 1st-Order Linear Systems](class-notes/Stability Analysis of 1st-Order Linear Systems.pdf){target="_blank"} | Stability of Equilibrium | - | - |
| **10** | Tu 10/31 | Review | Exam 2 Examples | - | Exam 2 Guide |
|  | Th 11/2 | **Exam 2** | - | - | - |
| **11** | Tu 11/7 | [Higher-Order ODEs & Characteristic Equations](class-notes/Higher-Order ODEs & Characteristic Equations.pdf){target="_blank"} | Homogeneous and Nonhomogeneous Solutions | - | - |
|  | Th 11/9 | [Undetermined Coefficients](class-notes/Undetermined Coefficients.pdf){target="_blank"} | Determining the Undetermined | Assigned: Homework 5 | - |
| **12** | Tu 11/14 | [Variation of Parameters](class-notes/Variation of Parameters.pdf){target="_blank"} | Varying the Parameters | - | - |
|  | Th 11/16 | Laplace Transforms | Transforming Derivatives à la Laplace | Assigned: Homework 6 | - |
| **13** | Tu 11/21 | Equilibrium Stability, &<br>Graphical Approaches of Higher-Order ODEs | TBA | - | - |
|  | Th 11/23 | _Thanksgiving Vacation_ | - | - | - |
| **14** | Tu 11/28 | Review | Exam 3 Examples | - | Exam 3 Guide  |
|  | Th 11/30 | **Exam 3** | - | - | - |
| **15** | Tu 12/5 | Power Series and Fourier Series Methods | - | All Revisions & Retakes Due | - |
|  | Th 12/7 | Non-Linear Systems of ODEs | Final Exam Examples | - | Final Exam Guide |
| **16** | Tu 12/12 | **Final Exam<br>Tu 1:30 PM - 3:30 PM** | - | - | - |

<br>

## **Books & Online Resources Lists**

```{r echo=FALSE}
refs <- bibtex::read.bib("references.bib")
```

*Click on the link to access the resources.*

### Textbooks

[H] [`r capture.output(print(refs["hallstrom2018"]))`](https://drive.google.com/file/d/12G9cs0RQPqiXb7vjJXVH58ePJ8DZBgC1/view?usp=sharing){target="_blank"}

[T] [`r capture.output(print(refs["trench2013elementary"]))`](https://digitalcommons.trinity.edu/cgi/viewcontent.cgi?article=1007&context=mono){target="_blank"}

### Websites

[C] `r capture.output(print(refs["clontz2022"]))`

[P] `r capture.output(print(refs["paulodenotes"]))`

<br>

# References

<div id="refs"></div>

<br>
