---
title: "Tentative Topics Schedule"
author: |
  | MTH-321 Section B
  | Fall 2023
  | University of Portland
  | Alex John Quijano
bibliography: references.bib
csl: apa.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source(file.path("R","functions.R"))
```

```{r echo=FALSE}
create_footer()
```

<br>

> See Books & Online Resources Lists for the reading materials.
>
> The readings are not mandatory but it is encouraged.

<br>The "Reading" column in the table below contains page number on which it refers to a label in the Books & Online Resources List. For example "Pgs. 1-5 [H]" refers to pages 1-5 of the first item in the list, which is the textbook titled "Ordinary Differential Equations: A Primer on Dynamics and Systems".

<br>

## **Topics and Materials**

| **Week** | **Day** | **Topic** | **Activity** | **Homework** | **Reading** |
|---|---|:---:|---|---|---|
| **1** | Tu 8/29 | Introduction & Orientation to Ordinary Differential Equations (ODEs) | Calculus Review | - | Syllabus |
|  | Th 8/31 | Modeling Physical Processes,<br>Classification of Equations, &<br>Verifying Solutions | Qualitative & Graphical Approaches | Assigned: Homework 1 | Sections 1.1.1. 1.2.3, & 1.2.5 [H]<br>Section 10.1 [T] |
| **2** | Tu 9/5 | Equilibrium,<br> Stability, &<br> Numerical Solutions | A Numerical Approach | - | TBA |
|  | Th 9/7 | Initial Value Problem (IVP),<br> Types of Solutions, &<br> Analytical Solutions | An Analytic Approach | Assigned: Homework 2 | TBA |
| **3** | Tu 9/12 | Solving 1st Order ODEs | Linear Differential Equations | - | TBA |
|  | Th 9/14 | Existence and Uniqueness of 1st Order IVP | Uniqueness of Solutions | Assigned: Homework 3 | TBA |
| **4** | Tu 9/19 | Analyzing Autonomous ODEs | Modeling with Autonomous Differential Equations | - | TBA |
|  | Th 9/21 | Bifurcations in One Dimension | The Effect of Varying a Parameter in Autonomous Differential Equations | Assigned: Homework 4  | TBA |
| **5** | Tu 9/26 | Review & Practice Exam | - | - | Exam 1 Guide |
|  | Th 9/28 | **Exam 1** | - | - | - |
| **6** | Tu 10/3 |  |  |  |  |
|  | Th 10/5 |  |  |  |  |
| **7** | Tu 10/10 |  |  |  |  |
|  | Th 10/12 |  |  |  |  |
| **8** | Tu 10/17 | _Fall Break_ |  |  |  |
|  | Th 10/19 | _Fall Break_ |  |  |  |
| **9** | Tu 10/24 |  |  |  |  |
|  | Th 10/26 |  |  |  |  |
| **10** | Tu 10/31 |  |  |  |  |
|  | Th 11/2 | **Exam 2** |  |  |  |
| **11** | Tu 11/7 |  |  |  |  |
|  | Th 11/9 |  |  |  |  |
| **12** | Tu 11/14 |  |  |  |  |
|  | Th 11/16 |  |  |  |  |
| **13** | Tu 11/21 |  |  |  |  |
|  | Th 11/23 | _Thanksgiving Vacation_ |  |  |  |
| **14** | Tu 11/28 |  |  |  |  |
|  | Th 11/30 | **Exam 3** |  |  |  |
| **15** | Tu 12/5 | Review |  |  |  |
|  | Th 12/7 | Review |  |  |  |
| **16** | Tu 12/12 | **Final Exam<br>Tu 1:30 PM - 3:30 PM** |  |  |  |

<br>

## **Books & Online Resources Lists**

```{r echo=FALSE}
refs <- bibtex::read.bib("references.bib")
```

*Click on the link to access the resources.*

### Textbooks

[H] [`r capture.output(print(refs["hallstrom2018"]))`](https://drive.google.com/file/d/12G9cs0RQPqiXb7vjJXVH58ePJ8DZBgC1/view?usp=sharing){target="_blank"}

[T] [`r capture.output(print(refs["trench2013elementary"]))`](https://digitalcommons.trinity.edu/cgi/viewcontent.cgi?article=1007&context=mono){target="_blank"}

### Websites

[C] `r capture.output(print(refs["clontz2022"]))`

[P] `r capture.output(print(refs["paulodenotes"]))`

<br>
