\documentclass[12pt,letterpaper,answers]{exam}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{tcolorbox}
\usepackage{geometry}

%% SOLUTION COMMANDS (BEGIN)

% TRIGGER SOLUTIONS
%\printanswers
\noprintanswers

% SOLUTION BOXES COLOURIZED
\usepackage{color}
\shadedsolutions
\definecolor{SolutionColor}{rgb}{0.8,0.9,1}

%% SOLUTION COMMANDS (END)

%% FOR PLOTTING (END)
\usepackage{pgfplots}
\pgfplotsset{compat = newest}
%% FOR PLOTTING (END)

\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\newcommand\vs{\vspace{0.70 in}}

\begin{document}
\cfoot{Page \thepage}
\rhead{MTH-321}

\textsc{Name(s):} \\

\begin{tabular}{l @{\hskip 8mm} l @{\hskip 8mm} l @{\hskip 8mm} l @{\hskip 8mm} l @{\hskip 8mm} l @{\hskip 8mm} l @{\hskip 8mm} l}
 {\bf } & I & NMI & NI & A & E & O \\
\end{tabular} \\

\textbf{Worksheet: Calculus Review} \\

The purpose of this worksheet is to review the essential concepts of calculus I and calculus II that are necessary for a successful start in differential equations. The problems are designed to help students practice their skills in limits, derivatives, series, and integrals. \\

\textbf{Instructions:} Worksheets are graded mostly on completion and partially on correctness. Please write your complete solutions on a separate paper.

\vspace{5mm} 
\hrule
 \vspace{5mm}
 
  \vspace{10mm}

\textbf{Part 1: Differentiation} \\

\begin{questions}
\question Differentiate the following functions with respect to x:

	\begin{parts}
		\part $f(x) = 3x^2 - 5x + 2$
		\part $g(x) = \sqrt{x} + \frac{1}{x}$
	\end{parts}

\question Find the equation of the tangent line to the curve $y = 2x^3 - x^2 + 3$ at the point where $x = 1$.

\question Determine the critical points of the function $h(x) = x^4 - 8x^2$, and classify each point as a local maximum, local minumum, or saddle point.

\question Compute the second derivative of $y = e^{2x} \sin{(x)}$.
\end{questions}

\newpage

\textbf{Part 2: Integration} \\

\begin{questions}
\question Evaluate the definite integral: $$\int_1^3 (3x^2 - 2x + 1) dx$$

\question Integrate the following using integration by parts: $$\int x \ln{(x)} dx$$

\question Compute the indefinite integral: $$\int \left(2e^x + \frac{1}{x} \right) dx$$

\question Evaluate the improper integral: $$\int_{1}^{\infty} \frac{1}{x^2} dx$$
\end{questions}

\newpage

\textbf{Part 3: Series} \\

\begin{questions}
\question Determine whether the sequence $a_n$ defined by $a_n = \frac{2^n}{n!}$ is convergent or divergent.

\question Find the sum of the geometric series: $$\sum_{n=0}^{\infty} \frac{1}{3^n}$$

\question Compute the sum of the first $n$ terms of the arithmetic series: $$4 + 8 + 12 + \cdots$$

\question Determine the interval of convergence for the power series: $$\sum_{n=0}^{\infty} \frac{(x-1)^n}{n}$$

\end{questions}

\newpage

\textbf{Outstanding Question} \\

\begin{questions}
\question Consider the integral: $$I = \int_{-\infty}^{\infty} e^{-x^2} dx$$

Use a Taylor series expansion for $e^{-x^2}$ and calculate the  value of the integral I using the first few terms of the series. Compare the result to the known value of $\sqrt{\pi}$. Explain the convergence properties of the series for this integral.

\end{questions}


\end{document}
